---
title: "Feb 13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("~/Documents/DATA Analysis")
library(dplyr)
library(reader)
library(ggplot2)
library(knitr)
Birds <- read.csv("Birds.csv", stringsAsFactors = FALSE)
BirdNames <- read.csv("BirdNames.csv", stringsAsFactors = FALSE)
```

```{r}
Birds2 <- Birds %>% 
  select(SpeciesName, Month, Day) %>% 
  mutate(Month = as.numeric(as.character(Month)), Day = as.numeric(as.character(Day)))
table(Birds$Month)
```

# Filter out the bad month

```{r}
Birds <- Birds %>% 
  filter(Month < 25)
table(Birds$Month)
```

# Let's clean up the bad spelling, First, count # distinct species

```{r}
n_distinct(BirdNames$SpeciesNameCleaned)
length(BirdNames$SpeciesName)
```


# Join the two tables together because there are bad names. 
```{r}
Corrected <- Birds %>% 
  inner_join(BirdNames)%>%
  select(Species = SpeciesNameCleaned, Month, Day)%>%
  na.omit()


```
# Let's display a table with Species and counts only. count the numbers of each species. 

```{r}
Count2 <- Corrected %>% 
  group_by(Species)%>%
  summarise(count = length(Species))%>% 
  arrange(desc(count))
```
create a summary table and use count. count means picking names. 


```{r}
Major <- Corrected %>% 
  group_by(Species) %>%
  mutate(count = length(Species)) %>%
  filter(count > 1000 )%>%
  select(Species, Month, Day)
```

summarize create small table, mutate giant data set, and create new variable in that data set. 


#Bar plot! 
```{r}
MajorMonthCount <- Major%>% 
  group_by(Species, Month)%>%
  summarise(count = length(Species))
  
```

```{r}
MajorMonthCount %>% ggplot(aes(Month,count, fill= Species)) + 
  geom_bar(stat = "identity", position = "dodge") + 
  facet_wrap(~Species)
```

